---
title: "ARIMA forecasting for crop prices"
author: "Lian Wang"
date: "`r Sys.Date()`"
output: pdf_document
---
```{r Load packages, include=F}
library(tidyverse)
library(forecast) # for forecast, tsCV
library(ggplot2)
library(tseries) # adf.test
#library(astsa)
#library(stats)
#library(TidyDensity)
library(paletteer)

```
```{r Define some custom functions, include=F}
alpha <- 0.05

test_bonferroni <- function(d){
  acf_values <- acf_res$acf[-1]
  num_lags <- length(acf_values)
  print(sprintf("Number of significant lags if white noise: %s", num_lags * alpha))
}

```

```{r, include=F}
# Load data and convert to long format
og <- read.csv("merged_data.csv")
og$DATE <- as.Date(og$DATE)

data <- og
# Log data to stabilize variance
#data[2:5] <- log(data[2:5])

data_long <- data %>%
  pivot_longer(cols = c(maize, soy, wheat, barley), names_to = "crop", values_to = "value")

# Convert data to ts matrix
data_ts <- data %>% 
  column_to_rownames("DATE") %>% 
  as.matrix()

# Separate ts for each crop
ts_barley <- ts(data$barley, start = c(1990, 1), frequency = 12)
ts_maize <- ts(data$maize, start = c(1990, 1), frequency = 12)
ts_soy <- ts(data$soy, start = c(1990, 1), frequency = 12)
ts_wheat <- ts(data$wheat, start = c(1990, 1), frequency = 12)
```

```{r Split train and test}
get_train <- function(ts) head(ts, round(length(ts) * 0.8))
get_test <- function(ts, ts_train) tail(ts, length(ts) - length(ts_train))

soy_train <- get_train(ts_soy)
soy_test <- get_test(ts_soy, soy_train)

barley_train <- get_train(ts_barley)
barley_test <- get_test(ts_barley, barley_train)

wheat_train <- get_train(ts_wheat)
wheat_test <- get_test(ts_wheat, wheat_train)

maize_train <- get_train(ts_maize)
maize_test <- get_test(ts_maize, maize_train)

train_length <- length(soy_train)
test_length <- length(soy_test)

```

\section{Preliminary}
```{r Plot all time series, echo=F}
# Plot data
ggplot(data_long, aes(x = DATE, y = value, color = crop)) +
  geom_line() +
  labs(title = "Crop prices over time", x = "Date", y = "Price", color = "Crop")+
  theme_minimal() +
  #scale_color_manual(values=c("dodgerblue","darkorange","forestgreen","#F4A460")) +
  #scale_color_brewer(palette = "RdBu")
  scale_color_paletteer_d("vangogh::CafeDeNuit")
#ggsave(filename = "plots/all_crops.png", width=10, height=6)

```

\section{Define functions}
```{r Model definitions}
fixed_model_pred <- function(ts_train, ts_test){
  ts_train <- soy_train
  ts_test <- soy_test
  
  # Get residuals from linear model fit on training set
  fitted_test <- pred_lm_test(ts_train, ts_test)
  res_test <- ts_test - fitted_test
  fitted_train <- pred_lm(ts_train)
  res_train <- ts_train - fitted_train
  
  # Fit ARIMA model on training set
  arima_model <- auto.arima(res_train)
  print(summary(arima_model))
  rmse <- sqrt(mean(arima_model$residuals^2))
  aic <- arima_model$aic

  # Forecast using model on test time points
  forecast <- forecast(arima_model, length(res_test))
  p_res <- get_mse_and_plot(arima_model$fitted, forecast$mean, res_train, res_test)
  
  # Add fitted values back to linear trend and plot
  p <- get_mse_and_plot(pred_train=arima_model$fitted + fitted_train, 
                        pred_test=forecast$mean + fitted_test, 
                        actual_train=ts_train, 
                        actual_test=ts_test)
  
  # Get MSE of the entire ts after exponentiating
  l <- get_mse_log(pred_train=arima_model$fitted + fitted_train, 
                   pred_test=forecast$mean + fitted_test,
                   unlogged=og$soy)

  return(list(p=p, log=l))
}

# ts <- ts_soy
# ts_train <- soy_train
# ts_test <- soy_test

rolling_model_pred <- function(ts, ts_train, ts_test, order, seasonal){
  # 
  # ts_train <- soy_train
  # ts_test <- soy_test
  # ts <- ts_soy
  # order <- c(1,0,0)
  # seasonal <- c(0,1,0)
  
  # Get residuals from linear model fit on training set
  fitted_test <- pred_lm_test(ts_train, ts_test)
  res_test <- ts_test - fitted_test
  fitted_train <- pred_lm(ts_train)
  res_train <- ts_train - fitted_train
  res <- ts(c(res_train, res_test),start=start(res_train), frequency=frequency(res_train))
  

  # Define rolling forecasting function
  forecast_fun <- function(x,h){
    model <- Arima(x, order=order, seasonal=seasonal)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    #aics <<- c(aics, aic)
    #rmses <<- c(rmses, rmse)
    return(forecast(model,h=h))
  }

  # Cross validation MSE
  e <- tsCV(res, forecast_fun, h=1)
  #print(e)
  
  mse_all <- mean(e^2, na.rm = T)
  e_test <- e[(1+test_length):length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  forecasted_vals <- res - e

  pred_train <- window(forecasted_vals, end=c(2017,10))
  pred_test <- window(forecasted_vals, start=c(2017,11))
  
  p_res <- get_mse_and_plot(pred_train=pred_train, 
                        pred_test=pred_test, 
                        actual_train=res_train, 
                        actual_test=res_test)

  pred_train <- pred_train + fitted_train
  pred_test <- pred_test+fitted_test
  # Add fitted values and plot
  p <- get_mse_and_plot(pred_train=pred_train, 
                        pred_test=pred_test, 
                        actual_train=ts_train, 
                        actual_test=ts_test)

  l <- get_mse_log(pred_train=pred_train , 
                   pred_test=pred_test, 
                   unlogged=og$soy)

  return(list(p=p, log=l))
}

rolling_model_exog_pred <- function(ts, ts_train, ts_test, order, seasonal, xreg){
  # Get residuals from linear model fit on training set
  fitted_test <- pred_lm_test(ts_train, ts_test)
  res_test <- ts_test - fitted_test
  fitted_train <- pred_lm(ts_train)
  res_train <- ts_train - fitted_train
  res <- ts(c(res_train, res_test),start=start(res_train), frequency=frequency(res_train))
  
  forecast_fun <- function(x,h, xreg, newxreg){
    model <- Arima(x, order=order, seasonal=seasonal, xreg=xreg)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    #aics <<- c(aics, aic)
    #rmses <<- c(rmses, rmse)
    return(forecast(model,h=h, xreg=newxreg))
  }
  
  e <- tsCV(res, forecastfunction = forecast_fun, h=1, xreg=xreg)
  forecasted_vals <- res - e
  
  pred_train <- window(forecasted_vals, end=c(2017,10))
  pred_test <- window(forecasted_vals, start=c(2017,11))

  p_res <- get_mse_and_plot(pred_train=pred_train, 
                      pred_test=pred_test, 
                      actual_train=res_train, 
                      actual_test=res_test)

  # Add fitted values and plot
  pred_train <- pred_train + fitted_train
  pred_test <- pred_test + fitted_test
  
  p <- get_mse_and_plot(pred_train=pred_train,
                      pred_test=pred_test,
                      actual_train=ts_train, 
                      actual_test=ts_test)
  
  l <- get_mse_log(pred_train=pred_train , 
                   pred_test=pred_test, 
                   unlogged=og$soy)

  return(list(p=p, log=l))
}


```

```{r Auxiliary functions}
pred_lm <- function(ts){
  linear_model <- lm(ts~time(ts))
  return(predict(linear_model))
}

pred_lm_test <- function(ts_train, ts_test){
  df <- data.frame(time=time(ts_train), value=as.numeric(ts_train))
  linear_model <- lm(value~time, df)
  pred <- sapply(time(ts_test), function(t){
    b <- coef(linear_model)[[1]]
    m <- coef(linear_model)[[2]]
    m*t + b
  })
  return(pred)
}

get_mse_and_plot <- function(pred_train, pred_test, actual_train, actual_test){
  forecast <- ts(c(pred_train, pred_test), 
                 start=start(pred_train), frequency=frequency(pred_test))
  
  actual <- ts(c(actual_train, actual_test), 
               start=start(actual_train), frequency=frequency(actual_test))
  
  p <- autoplot(actual, series="actual") +
    autolayer(forecast, series="predicted") +
    geom_vline(xintercept=time(pred_test)[1], linetype="dashed", color="black") +
    scale_color_manual(values=c("actual"="dodgerblue", "predicted"="darkorange")) +
    labs(y="price") +
    theme_minimal()+
    guides(color = guide_legend(title = NULL))
    

  # Get CV MSE
  e_train <- pred_train- actual_train
  e_test <- pred_test - actual_test
  mse_test <- mean(e_test^2, na.rm=T)
  mse_all <- mean(c(e_test^2, e_train^2), na.rm=T)
  print(sprintf("residuals MSE overall: %s | MSE test: %s", round(mse_all,3), round(mse_test,3)))
  
  return(list(plot=p, mse_test=mse_test, mse_all=mse_all))
}

get_mse_log <- function(pred_train, pred_test, unlogged){
  pred_test <- exp(pred_test)
  pred_train <- exp(pred_train)
  og_train <- get_train(unlogged)
  og_test <- get_test(unlogged, og_train)
  return(mean(na.omit((og_test-as.vector(pred_test)))^2+na.omit((og_train-as.vector(pred_train)))^2))
}

create_lag <- function(ts_data, lag = 1) {
  c(rep(NA, lag), ts_data[1:(length(ts_data) - lag)])
}
```

```{r Define forecasting functions}
forecast_arima <- function(ts, order, seasonal){
  # Define forcast function
  forecast_fun <- function(x,h){
    model <- Arima(x, order=order, seasonal = seasonal)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    #aics <<- c(aics, aic)
    #rmses <<- c(rmses, rmse)
    return(forecast(model,h=h))
  }
  
  # Get MSE of test set and forecasted values
  e <- tsCV(ts, forecast_fun, h=1)
  print(e)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  forecasted_vals <- ts - e
  return(list(mse_test, forecasted_vals))
}

forecast_auto_arima <- function(ts){
  # Define forcast function
  forecast_fun <- function(x,h){
    model <- auto.arima(x)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    aics <<- c(aics, aic)
    rmses <<- c(rmses, rmse)
    forecast(model,h=h)
  }
  
  # Get MSE of test set and forecasted values
  e <- tsCV(ts, forecast_fun, h=1)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  forecasted_vals <- ts - e
  return(list(mse_test, forecasted_vals))
}


```
```{r Forecast other crops}
res_barley <- ts_barley - pred_lm(ts_barley)
m <- auto.arima(res_barley)
m
m$arma
l <- forecast_arima(res_barley, c(1,2,0), c(0,0,0))
mse <- l[[1]]
res_barley_pred <- l[[2]]
autoplot(res_barley, series="actual") + 
  autolayer(res_barley_pred, series="forecasted") +
  ggtitle(sprintf("Barley; ARIMA(1,0,2)(2,0,0), rolling; MSE=%s", round(mse,3)))
#ggsave("plots/log_barley_arima102200.png")

res_wheat <- ts_wheat - pred_lm(ts_wheat)
m <- auto.arima(res_wheat)
m
m$arma
l <- forecast_arima(res_wheat, c(1,0,1), c(0,0,0))
mse <- l[[1]]
res_wheat_pred <- l[[2]]
autoplot(res_wheat, series="actual") + 
  autolayer(res_wheat_pred, series="forecasted") +
  ggtitle(sprintf("Wheat; ARIMA(1,0,1)(0,0,1), rolling; MSE=%s", round(mse,3)))
#ggsave("plots/log_wheat_arima101001.png")

res_maize <- ts_maize - pred_lm(ts_maize)
m <- auto.arima(res_maize)
m
m$arma
l <- forecast_arima(res_maize, c(2,0,0), c(0,0,0))
mse <- l[[1]]
res_maize_pred <- l[[2]]
autoplot(res_maize, series="actual") + 
  autolayer(res_maize_pred, series="forecasted") +
  ggtitle(sprintf("Maize; ARIMA(1,1,0), rolling; MSE=%s", round(mse,3)))
#ggsave("plots/log_maize_arima110.png")

res_soy <- ts_soy - pred_lm(ts_soy)
m <- auto.arima(res_soy)
m
m$arma
l <- forecast_arima(res_soy, c(1,0,2), c(0,0,0))
mse <- l[[1]]
res_soy_pred <- l[[2]]

# Get train and test splits
res_barley_train <- get_train(res_barley)
res_barley_test <- get_test(res_barley, res_barley_train)
res_wheat_train <- get_train(res_wheat)
res_wheat_test <- get_test(res_wheat, res_wheat_train)
res_maize_train <- get_train(res_maize)
res_maize_test <- get_test(res_maize, res_maize_train)
res_soy_train <- get_train(res_soy)
res_soy_test <- get_test(res_soy, res_soy_train)
```

\section{Forecast soy}
```{r Forecast soy}
# order <- arima_model$arma[1:3]
# seasonal <- arima_model$arma[c(4,6,7)]
m <- auto.arima(soy_train)
summary(m) # (1,0,0)(0,1,0) for non logged model

# Fixed model forecasting
result <- fixed_model_pred(soy_train, soy_test)
title <- sprintf("ARIMA(1,1,0), fixed; MSE=%s",round(result$p$mse_test,2))
result$p$plot + ggtitle(title)
#ggsave("plots/arima110_fixed.png", dpi=300, width=7.5, height=5)

# One-step ahead forecasting with (1,0,0)(0,1,0)
order <- c(1,1,0)
seasonal <- c(0,0,0)
result <- rolling_model_pred(ts_soy, soy_train, soy_test, order=order, seasonal=seasonal)
title <- sprintf("ARIMA(1,1,0), rolling; MSE=%s", round(result$p$mse_test,2))
result$p$plot + ggtitle(title)
#ggsave("plots/arima110.png", dpi=300, width=7.5, height=5)

# One-step ahead forecasting with exogenous variables
xreg_train <- cbind(res_barley_train, res_wheat_train, res_maize_train)
r <- (1+train_length):length(res_barley_pred)
xreg_test <- cbind(res_barley_pred[r], res_wheat_pred[r], res_maize_pred[r])
xreg <- rbind(xreg_train, xreg_test)

model <- auto.arima(res_train, xreg=xreg_train)
summary(model)
order <- c(1,0,2)
seasonal <- c(0,0,1)
result <- rolling_model_exog_pred(ts_soy, soy_train, soy_test, order=order, seasonal=seasonal, xreg=xreg)
title <- sprintf("ARIMA(1,0,2)(0,0,1) with exog, rolling; MSE=%s", round(result$log,2))
result$p$plot + ggtitle(title)
#ggsave("plots/log_arima102001_exog.png", dpi=300, width=7.5, height=5)

# One-step ahead forecasting with 1- and 2-lagged exogenous variables (forecasted values)
xreg_train <- cbind(
  create_lag(res_maize_train, lag = 1),
  create_lag(res_barley_train, lag = 1),
  create_lag(res_wheat_train, lag = 1)
)
xreg_test <- cbind(
  create_lag(res_maize_test, lag = 1),
  create_lag(res_barley_test, lag = 1),
  create_lag(res_wheat_test, lag = 1)
  # create_lag(res_barley_pred[r], lag = 1),
  # create_lag(res_wheat_pred[r], lag = 1),
  # create_lag(res_maize_pred[r], lag = 1),
  # create_lag(res_barley_pred[r], lag = 2),
  # create_lag(res_wheat_pred[r], lag = 2),
  # create_lag(res_maize_pred[r], lag = 2)
)
xreg <- rbind(xreg_train, xreg_test)

model <- auto.arima(res_train, xreg=xreg_train)
summary(model)
order <- c(2,0,0)
seasonal <- c(0,0,0)
result <- rolling_model_exog_pred(ts_soy, soy_train, soy_test, order=order, seasonal=seasonal, xreg=xreg)
title <- sprintf("ARIMA(2,1,0) with current time horizon, rolling; MSE=%s", round(result$p$mse_test,2))
result$p$plot + ggtitle(title)
#ggsave("plots/arima200_lag1_actual.png", dpi=300, height=5, width=7.5)

######
ggAcf(diff(res)) +
  ggtitle("Differenced soy residuals")+
  theme_minimal()

ggAcf(diff(res_train)) +
  ggtitle("Differenced soy (train) residuals")+
  theme_minimal()

ggAcf(diff(res_test)) +
  ggtitle("Differenced soy (test) residuals")+
  theme_minimal()

```


\section{Preliminary}
We have monthly time series data from January 1990 to October 2024 for the prices of four crops: barley, maize, soy, and wheat. Based on the plot, it is clear that the four time series are correlated, where there are peaks and troughs that are roughly shared between the crops. We are interested in modeling the price of soy, possibly exploiting the correlations with other time series to improve model fit. 

```{r, echo=F}
# Plot data
ggplot(data_long, aes(x = DATE, y = value, color = crop)) +
  geom_line() +
  labs(title = "Crop prices over time", x = "Date", y = "Price", color = "Crop")+
  theme_minimal()
```


\subsection{Linear detrending}
The prices for all crops are clearly increasing over time, so we first detrend each time series by fitting a linear model. We will now work with the residuals from the linear model, which have mean 0 by construction. We examine the ACF and PACF plot of the residuals of each series. The ACF plots have a decreasing slope over lag size, suggesting that there is autocorrelation structure in the data that decays over time. This suggests that we can difference the data. The PACF for different lags have smaller autocorrelation, but there is a slight periodic structure, where autocorrelation alternates between positive and negative. This suggests that we should fit a model that can capture seasonality, e.g. a SARIMA model.


```{r}
# Linear trend on whole data
detrend <- function(ts, crop){
  par(mfrow=c(2,2), mar = c(2, 4, 2, 2), oma = c(1, 1, 1, 1))

  # Fit linear trend
  linear_model <- lm(ts~time(ts))
  sm <- summary(linear_model)
  print(sm)
  plot(ts, ylab=sprintf("%s price", crop), main=sprintf("%s time series",crop))
  abline(linear_model, col="blue")
  
  # Residuals after linear detrending
  res <- ts - predict(linear_model)
  plot(res, main="Residuals")
  acf(res, main="")
  pacf(res, main="")
  
  return(res)
}

res_barley <- detrend(ts_barley, "Barley")
res_wheat <- detrend(ts_wheat, "Wheat")
res_maize <- detrend(ts_maize, "Maize")
res_soy <- detrend(ts_soy, "Soy")
#test_bonferroni(res_barley)


# Linear trend on train, detrend test
get_split_res <- function(ts_train, ts_test){
  df <- data.frame(time=time(ts_train), value=as.numeric(ts_train))
  linear_model <- lm(value~time, df)
  pred <- sapply(test_time, function(t){
    b <- coef(linear_model)[[1]]
    m <- coef(linear_model)[[2]]
    m*t + b
  })
  
  res_train <- ts_train - linear_model$fitted.values
  res_test <- ts_test - pred
  return(list(res_train, res_test))
}

res_soy_train <- get_split_res(soy_train, soy_test)[[1]]
res_soy_test <- get_split_res(soy_train, soy_test)[[2]]

res_barley_train <- get_split_res(barley_train, barley_test)[[1]]
res_barley_test <- get_split_res(barley_train, barley_test)[[2]]

res_maize_train <- get_split_res(maize_train, maize_test)[[1]]
res_maize_test <- get_split_res(maize_train, maize_test)[[2]]

res_wheat_train <- get_split_res(wheat_train, wheat_test)[[1]]
res_wheat_test <- get_split_res(wheat_train, wheat_test)[[2]]
```
\subsection{Differencing}
After first-order differencing the residuals for each of the crops, we no longer see the decreasing slope in the ACF plot. Instead, most of the autocorrelations now are within the confidence bounds for white noise and roughly follow a periodic structure. Thus what remains is to model the periodic structure.

```{r}
difference <- function(ts, crop, order){
  diff_ts <- diff(ts, differences = order)
  
  par(mfrow=c(2,2), mar = c(2, 4, 2, 2), oma = c(1, 1, 1, 1))
  plot(ts, main=sprintf("%s residuals", crop), xlab="Residuals")
  plot(diff_ts, main=sprintf("After %s month differencing", order), xlab="Differenced residuals")
  acf(diff_ts, main="")
  pacf(diff_ts, main="")
  
  return(diff_ts)
}

diff_soy <- difference(res_soy, "Soy", 1)
diff_wheat <- difference(res_wheat, "Wheat", 1)
diff_maize <- difference(res_maize, "Maize", 1)
diff_barley <- difference(res_barley, "Barley", 1)

diff_soy_train <- difference(res_soy_train, "Soy (train)", 1)
diff_soy_test <- difference(res_soy_test, "Soy (test)", 1)

```

We can also use the Augmented Dickey-Fuller test to test the stationarity of the time series, where we test the null hypothesis that the time series is not stationary, thus a lower p-value is evidence that the time series is stationary. All of the residuals before differencing had $p>0.05$, whereas all of the differenced residuals had $p<0.01$.
```{r, warning=F}
paste("P-value, soy residuals:", round(adf.test(res_soy)$p.value,3))
paste("P-value, wheat residuals:", round(adf.test(res_wheat)$p.value,3))
paste("P-value, maize residuals:", round(adf.test(res_maize)$p.value,3))
paste("P-value, barley residuals:", round(adf.test(res_barley)$p.value,3))

paste("P-value, differenced soy residuals:", round(adf.test(diff_soy)$p.value,3))
paste("P-value, differenced wheat residuals:", round(adf.test(diff_wheat)$p.value,3))
paste("P-value, differenced maize residuals:", round(adf.test(diff_maize)$p.value,3))
paste("P-value, differenced barley residuals:", round(adf.test(diff_barley)$p.value,3))

```

While it is not strictly necessary to separately difference the data, as I subsequently use \texttt{auto.arima}, which includes differencing terms, I've found that first-order differencing before fitting an \texttt{auto.arima} improves fit.

\section{SARIMA}
\subsection{On differenced time series}
We will now focus on fitting the time series data for soy prices, specifically the first-order differenced residuals from the linear model. This section fits a SARIMA model to the data.
```{r AR(1) with fixed coefficients}
# Forecast next 84 months using same model with same coefficients
# Fit ARIMA model on training set
d <- diff_soy_train
d_arima <- auto.arima(d) 
summary(d_arima)
rmse <- sqrt(mean(d_arima$residuals^2))
paste("Model AIC:", round(d_arima$aic,3), "; RMSE:", round(rmse,3))

# Plot forecasts
future <- forecast(d_arima, test_length)
autoplot(diff_soy) +
  autolayer(d_arima$fitted, series="Fitted values") +
  autolayer(future$mean, series="Predicted future values") +
  ggtitle("AR(1) model with fixed coefficients")

# Get MSE
e_train <- d_arima$fitted - diff_soy_train
e_test <- future$mean - diff_soy_test
mse_test <- mean(e_test^2, na.rm=T)
mse_all <- mean(c(e_test^2, e_train^2), na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))
```

```{r}
# Rolling Forecast Implementation
rolling_forecast <- function(train, test, h = 1) {
  forecasts <- numeric(length(test))  # To store forecasts
  training_set <- train               # Start with the training data
  
  for (i in seq_along(test)) {
    # Fit the ARIMA model on the current training set
    model <- auto.arima(training_set)
    
    # Forecast the next value (h=1)
    forecast_value <- forecast(model, h = h)$mean[1]
    
    # Store the forecasted value
    forecasts[i] <- forecast_value
    
    # Add the predicted value to the training set for the next iteration
    training_set <- c(training_set, forecasts[i])
  }
  
  # Return the forecasts
  return(forecasts)
}

# Example Use:
train <- diff_soy_train
test <- diff_soy_test

# Perform rolling forecast
forecasts <- rolling_forecast(train, test)
forecasts_ts <- ts(forecasts, start=start(test), frequency = frequency(test))
# Evaluate RMSE
mse <- mean((forecasts - test)^2)
mse

autoplot(test) + 
  autolayer(forecasts_ts)

```

```{r AR(1), rolling window}
# Forecast next 84 months using same model refitting coefs of AR(1) model, growing window size
d <- diff_soy
rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- Arima(x, order=c(1,0,0))
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h)
}

# Get MSE
e <- tsCV(d, forecast_fun, h=1)
mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- diff_soy - e
fitted <- window(forecasted_values, end=c(2017,10))
future <- window(forecasted_values, start=c(2017, 11))
autoplot(fitted) + 
  autolayer(future, series="predicted values") + 
  autolayer(diff_soy, series="actual values") +
  ggtitle("AR(1) model refitted with rolling window") 

autoplot(diff_soy_test, series="actual") + autolayer(future, series="predicted")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

```{r AR(1), fixed window}
# Forecast next 84 months using same model refitting coefs of AR(1) model, fixed window size of 5, 15, 50, 100, 150
d <- diff_soy
rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- Arima(x, order=c(1,0,0))
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h)
}

# Get MSE
for (w in c(5, 15, 50, 100, 150)){
  print(sprintf("window size=%s", w))
  e <- tsCV(d, forecast_fun, h=1, window=w)
  mse_all <- mean(e^2, na.rm=T)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  print(sprintf("MSE overall: %s | MSE test: %s", round(mse_all,3),round(mse_test,3)))
}

# Plot forecasted values
forecasted_values <- diff_soy - e
fitted <- window(forecasted_values, end=c(2017,10))
future <- window(forecasted_values, start=c(2017, 11))
autoplot(fitted) + autolayer(future, series="predicted values") + ggtitle("AR(1) model refitted with rolling window")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

```{r auto.arima, rolling window}
# Forecast next 84 months using auto.arima with each window
d <- diff_soy
rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- auto.arima(x)
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  #print(model$arma)
  forecast(model,h=h)
}

# Get MSE
e <- tsCV(d, forecast_fun, h=1)
mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- diff_soy - e
# fitted <- window(forecasted_values, end=c(2017,10))
# future <- window(forecasted_values, start=c(2017, 11))
autoplot(d) + 
  autolayer(forecasted_values, series="predicted") + 
  ggtitle("auto.arima on rolling window")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

```{r auto.arima, fixed window}
# Forecast next 84 months using auto.arima with each window
d <- diff_soy
rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- auto.arima(x)
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  #print(model$arma)
  forecast(model,h=h)
}

# Get MSE
for (w in c(5, 15, 50, 100, 150)){
  print(sprintf("window size=%s", w))
  e <- tsCV(d, forecast_fun, h=1, window=w)
  mse_all <- mean(e^2, na.rm=T)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  print(sprintf("MSE overall: %s | MSE test: %s", round(mse_all,3),round(mse_test,3)))
}

# Plot forecasted values
forecasted_values <- diff_soy - e
fitted <- window(forecasted_values, end=c(2017,10))
future <- window(forecasted_values, start=c(2017, 11))
autoplot(fitted) + autolayer(future, series="predicted values") + ggtitle("auto.arima on rolling window")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

\subsection{On non-differenced series}
```{r ARIMA(1,1,0) with fixed coefficients}
# Forecast next 84 months using same model with same coefficients
# Fit ARIMA model on training set
d <- res_soy_train
d_arima <- auto.arima(d) 
d_arima

rmse <- sqrt(mean(d_arima$residuals^2))
paste("AIC:", round(d_arima$aic,3), "; RMSE:", round(rmse,3))

# Plot forecasts
future <- forecast(d_arima, test_length)
forecasted <- ts(c(d_arima$fitted,future$mean), start=start(d_arima$fitted), frequency=frequency(d_arima$fitted))
autoplot(res_soy, series="actual") +
  autolayer(forecasted, series="predicted") +
  ggtitle("ARIMA(1,1,0), fixed coefficients") +
  geom_vline(xintercept=time(res_soy_test)[1], linetype="dashed", color="darkblue")


# Get MSE
e_train <- d_arima$fitted - d
e_test <- forecasted- res_soy_test
mse_test <- mean(e_test^2, na.rm=T)
mse_all <- mean(c(e_test^2, e_train^2), na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))
```

```{r use rolling_forecast function}
train <- res_soy_train
test <- res_soy_test

# Perform rolling forecast
forecasts <- rolling_forecast(train, test)
forecasts_ts <- ts(forecasts, start=start(test), frequency = frequency(test))
mse <- mean((forecasts - test)^2)
mse

autoplot(test) + 
  autolayer(forecasts_ts)

```

```{r ARIMA(1,0,0)(0,1,0)[12], rolling window}
d <- res_soy_train
d_arima <- auto.arima(d)
d_arima$arma

rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- Arima(x, order=c(1,0,0), seasonal=c(0,1,0))
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h)
}

# Get MSE
e <- tsCV(d, forecast_fun, h=1)
mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- d - e
fitted <- window(forecasted_values, end=c(2017,10))
future <- window(forecasted_values, start=c(2017, 11))
autoplot(fitted) + 
  autolayer(future, series="predicted values") + 
  autolayer(res_soy, series="actual")+
  ggtitle("AR(1) model refitted with rolling window")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

```{r ARIMA(1,1,0), rolling window}
d <- res_soy
d_arima <- auto.arima(res_soy_train)
d_arima$arma

rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- Arima(x, order=c(1,1,0))
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h)
}

# Get MSE
e <- tsCV(d, forecast_fun, h=1)
mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- d - e
# fitted <- window(forecasted_values, end=c(2017,10))
# future <- window(forecasted_values, start=c(2017, 11))
autoplot(res_soy, series="actual") + 
  autolayer(forecasted_values, series="predicted") + 
  ggtitle("ARIMA(1,1,0), rolling window") +
  geom_vline(xintercept=time(res_soy_test)[1], linetype="dashed", color="darkblue")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

```{r auto.arima, rolling window}
# Forecast next 84 months using auto.arima with each window
d <- res_soy
rmses <- c()
aics <- c()
forecast_fun <- function(x,h){
  model <- auto.arima(x)
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  #print(model$arma)
  forecast(model,h=h)
}

# Get MSE
e <- tsCV(d, forecast_fun, h=1)
mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- d - e
fitted <- window(forecasted_values, end=c(2017,10))
future <- window(forecasted_values, start=c(2017, 11))
autoplot(d) + autolayer(forecasted_values, series="predicted") + ggtitle("auto.arima on rolling window")

# Plot AIC and RMSE of models
plot(aics, type="l", main="AIC of models on rolling window", xlab="Model index", ylab="AIC")
plot(rmses, type="l", main="RMSE of models on rolling window", xlab="Model index", ylab="RMSE")
```

\section{SARIMAX (SARIMA with exogenous variables)}
Now we want to exploit the correlation between the crop prices in order to predict soy prices. We will again fit a SARIMA model, but this time using the differenced series for the other crops as exogenous variables, i.e. additional predictors. 
```{r Define forecasting functions}
forecast_arima <- function(ts, order, seasonal){
  # Define forcast function
  forecast_fun <- function(x,h){
    model <- Arima(x, order=order, seasonal = seasonal)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    aics <<- c(aics, aic)
    rmses <<- c(rmses, rmse)
    forecast(model,h=h)
  }
  
  # Get MSE of test set and forecasted values
  e <- tsCV(ts, forecast_fun, h=1)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  forecasted_vals <- ts - e
  return(list(mse_test, forecasted_vals))
}

forecast_auto_arima <- function(ts){
  # Define forcast function
  forecast_fun <- function(x,h){
    model <- auto.arima(x)
    aic <- summary(model)$aic
    rmse <- sqrt(mean(model$residuals^2))
    aics <<- c(aics, aic)
    rmses <<- c(rmses, rmse)
    forecast(model,h=h)
  }
  
  # Get MSE of test set and forecasted values
  e <- tsCV(ts, forecast_fun, h=1)
  e_test <- e[1+test_length:length(e)]
  mse_test <- mean(e_test^2, na.rm=T)
  forecasted_vals <- ts - e
  return(list(mse_test, forecasted_vals))
}


```
```{r Forecast other crops}
auto.arima(res_barley)$arma
l <- forecast_arima(res_barley, c(1,2,0), c(0,0,0))
mse <- l[[1]]
res_barley_pred <- l[[2]]
autoplot(res_barley, series="actual") + 
  autolayer(res_barley_pred, series="forecasted") +
  ggtitle("Barley")
paste("MSE:", mse)

auto.arima(res_wheat)$arma
l <- forecast_arima(res_wheat, c(1,1,0), c(0,0,0))
mse <- l[[1]]
res_wheat_pred <- l[[2]]
autoplot(res_wheat, series="actual") + 
  autolayer(res_wheat_pred, series="forecasted") +
  ggtitle("Wheat")
paste("MSE:", mse)

auto.arima(res_maize)$arma
l <- forecast_arima(res_maize, c(2,0,0), c(0,0,0))
mse <- l[[1]]
res_maize_pred <- l[[2]]
autoplot(res_maize, series="actual") + 
  autolayer(res_maize_pred, series="forecasted") +
  ggtitle("Maize")
paste("MSE:", mse)


```

```{r}
# Fit SARIMAX model with exogenous variables, refitting
xreg_train <- cbind(res_barley_train, res_wheat_train, res_maize_train)
r <- (1+train_length):length(res_barley_pred)
xreg_test <- cbind(res_barley_pred[r], res_wheat_pred[r], res_maize_pred[r])
xreg <- rbind(xreg_train, xreg_test)


auto.arima(res_soy, xreg=xreg)$arma
# forecast_fun <- function(x,h, xreg, newxreg){
#   forecast(Arima(x,xreg=xreg, order=c(1,2,0), seasonal=c(0,0,0)), xreg=newxreg, h=h)
# }
forecast_fun <- function(x,h, xreg, newxreg){
  model <- Arima(x, order=c(1,2,0), xreg=xreg)
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h, xreg=newxreg)
}

e <- tsCV(res_soy, forecastfunction = forecast_fun, h=1, xreg=xreg)

mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- res_soy - e
autoplot(res_soy, series="actual") + 
  autolayer(forecasted_values, series="predicted") +
  geom_vline(xintercept=time(res_soy_test)[1], linetype="dashed", color="darkblue") +
  ggtitle("One-step ahead with exogenous variables, rolling")
```

```{r}
# Fit SARIMAX model with exogenous variables ILLEGAL, refitting
xreg <- cbind(res_barley, res_wheat, res_maize)


auto.arima(res_soy, xreg=xreg)$arma
# forecast_fun <- function(x,h, xreg, newxreg){
#   forecast(Arima(x,xreg=xreg, order=c(1,2,0), seasonal=c(0,0,0)), xreg=newxreg, h=h)
# }
forecast_fun <- function(x,h, xreg, newxreg){
  model <- Arima(x, order=c(1,2,0),xreg=xreg)
  aic <- summary(model)$aic
  rmse <- sqrt(mean(model$residuals^2))
  aics <<- c(aics, aic)
  rmses <<- c(rmses, rmse)
  forecast(model,h=h, xreg=newxreg)
}

e <- tsCV(res_soy, forecastfunction = forecast_fun, h=1, xreg=xreg)

mse_all <- mean(e^2, na.rm=T)
e_test <- e[1+test_length:length(e)]
mse_test <- mean(e_test^2, na.rm=T)
paste("MSE overall:", round(mse_all,3), "| MSE test:", round(mse_test,3))

# Plot forecasted values
forecasted_values <- res_soy - e
autoplot(res_soy, series="actual") + 
  autolayer(forecasted_values, series="predicted") +
  geom_vline(xintercept=time(res_soy_test)[1], linetype="dashed", color="darkblue") +
  ggtitle("One-step ahead with exogenous variables ILLEGAL")
```

```{r}
exog <- cbind(diff_wheat, cbind(diff_barley, diff_maize))
d_arima <- auto.arima(diff_soy, xreg=exog)

res_arima <- residuals(d_arima)
summary(d_arima)
par(mfrow=c(2,2), mar = c(2, 4, 2, 2), oma = c(1, 1, 1, 1))
plot(res_arima, main="Residuals of ARIMA fit")
acf <- acf(res_arima, main="")
pacf <- pacf(res_arima, main="")
Box.test(res_arima, lag=20, type="Ljung-Box")
qqnorm(res_arima)
qqline(res_arima)
# xreg_future <- matrix(0, nrow=36, ncol=3)
# par(mfrow=c(1,1))
# plot(forecast(d_arima, 36, xreg = xreg_future), main="3 year forecast")

forecast_fun <- function(x,h, xreg, newxreg){
  forecast(auto.arima(x,xreg=xreg), xreg=newxreg, h=h)
}

# forecast_fun <- function(x,h,xreg,newxreg) {
#   y <- auto.arima(x, xreg=xreg) %>% 
#     forecast(xreg=newxreg, h=h)
#   y$mean <- y$mean[1:h]
#   return(y)
# }

m1 <- auto.arima(diff_soy)
m2 <- auto.arima(diff_soy,xreg=exog)
summary(m1)
summary(m2)
plot(auto.arima(diff_soy) %>% forecast())
plot(auto.arima(diff_soy, xreg=exog) %>% forecast(xreg=exog))

e <- tsCV(diff_soy, forecastfunction = forecast_fun, h=1, window=100, xreg=exog)
mse <- mean(e^2, na.rm=T)
paste("MSE: ", mse)

```


\section{Fourier transform}
```{r}

forecast_fun <- function(x,h, xreg, newxreg){
  forecast(auto.arima(x,xreg=xreg), xreg=newxreg, h=h)
}

# Just fourier terms as xreg
mses_dft <- sapply(1:6, function(K){
  print(K)
  dft <- fourier(diff_soy, K=K)
  
  model <- auto.arima(diff_soy, xreg=dft)
  summary(model)
  e <- tsCV(diff_soy, forecastfunction = forecast_fun, h=1, window=10, xreg=dft)
  mse <- mean(e^2, na.rm = T)

})
mses_dft

# Fourier terms + other crops as xreg
mses_all <- sapply(1:6, function(K){
  print(K)
  dft <- fourier(diff_soy, K=K)
  
  model <- auto.arima(diff_soy, xreg=cbind(dft, exog))
  summary(model)
  e <- tsCV(diff_soy, forecastfunction = forecast_fun, h=1, window=10, xreg=cbind(dft, exog))
  mse <- mean(e^2, na.rm = T)

})
mses_all


# 
# fft_result <- fft(diff_wheat)
# # Extract positive frequencies
# N <- length(fft_result)
# freq <- (0:(N / 2 - 1)) / N  # Frequency indices
# magnitude <- Mod(fft_result[1:(N / 2)])  # Magnitudes of positive frequencies
# 
# # Create a data frame for analysis
# fft_data <- data.frame(freq = freq, magnitude = magnitude)
# 
# # Plot frequency spectrum
# ggplot(fft_data, aes(x = freq, y = magnitude)) +
#   geom_line(color = "blue") +
#   labs(title = "Frequency Spectrum of the Crop Time Series",
#        x = "Frequency",
#        y = "Magnitude") +
#   theme_minimal()
# 
# f_k1 <- fourier(diff_wheat, K=1)
# f_k2 <- fourier(diff_wheat, K=2)
# f_k3 <- fourier(diff_wheat, K=3)
# 
# f1 <- function(x,h){
#   return(forecast(auto.arima(x)))
# }
# f2 <- function(x,h){
#   return(forecast(auto.arima(x, xreg=f_k3), xreg=xreg))
# }
# h=1
# cv_errors <- tsCV(diff_wheat, forecastfunction = f2, h=h, window=30, xreg=f_k3)
# mse <- mean(cv_errors^2, na.rm=T)
# mse

############
# fft_result <- fft(res_arima)
# # Extract positive frequencies
# N <- length(fft_result)
# freq <- (0:(N / 2 - 1)) / N  # Frequency indices
# magnitude <- Mod(fft_result[1:(N / 2)])  # Magnitudes of positive frequencies
# 
# # Create a data frame for analysis
# fft_data <- data.frame(freq = freq, magnitude = magnitude)
# 
# # Plot frequency spectrum
# ggplot(fft_data, aes(x = freq, y = magnitude)) +
#   geom_line(color = "blue") +
#   labs(title = "Frequency Spectrum of the Crop Time Series",
#        x = "Frequency",
#        y = "Magnitude") +
#   theme_minimal()

```

